### 2021-01-28 msc-thesis.tex
integration overview

\paragraph{1. Selection of Administrative Service}
The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

@@

\paragraph{3. Filling in Application}
Personal information from the user profile is used by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

\paragraph{4. Uploading Attachments}
The user can upload documents to his user profile and reference them in the form.

@@

\paragraph{8. Sending of Acknowledgment}
The data-exchange platform notifies the user through the inbox functionality of the user profile if the application was submitted successfully.

@@

@@

\paragraph{Administration Portal}
The administration portal provides the user access to various OZG services of other system components:

    \item \textbf{Application for administrative service}
    The administration portal provides access to services for creation and submission of applications for administration services. The portal hosts a web page for each administration service which enables the user to get information about the service and start the application process. After starting the process, the portal interacts with multiple system components to guide the user through the application.

    \item \textbf{Management of user profile}
    The administration portal provides access to the personal information stored in the user profile by interacting with the user profile system component. It enables the user to add, remove and update a set of attributes.

    \item \textbf{Management of inbox}
    The administration portal provides access to the inbox of the user profile. It enables the user to send new messages and display received messages.

    \item \textbf{Management of data wallet}
    The administration portal provides access to the data wallet of the user profile. It enables the user to upload and download documents and to attach copies of documents to applications.

The administration portal provides additional services:

\begin{itemize}
    \item \textbf{Determination of responsible institution}

    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender. It is the responsibility of the administration portal to determine which institution receives which application.

    \item \textbf{Search and find Administrative Service}

    The administration portal provides a search and find service which enables the user to find the web page of all administrative services which relate to the entered search term.

@@

\section{IMP Solution Proposal}

This section describes a solution for an IMP system considering the previously mentioned requirements.

\subsection{Components}

@@

The IMP client is a smartphone application which enables the user to manage his IMP identity. The client provides the following functionalities:
\begin{itemize}
    \item Create an identity
    \item Manage attributes of the identity
    \item Manage documents
    \item Send and receive messages
    \item Send and receive relationship requests
    \item Send and receive requests
\end{itemize}

\subsubsection{IMP Server}
The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
\begin{itemize}
    \item Create and store relationship template
    \item Create and store request template
    \item Deliver relationship requests
    \item Deliver requests
    \item Deliver messages
\end{itemize}

\subsection{Functionalities}

\subsubsection{Relationships}

\subsubsection{Requests}

@@

@@

\section{Integration}

Multiple integration scenarios are presented with increasing complexity and functionality.

\subsection{Scenario 1}

In this scenario, the IMP system integrates only with the administration portal to enable the usage of its identity related functionalities through the IMP client. The integration architecture contains one connector which interacts with the administration portal. The integration should provide an additional optional way for users to manage their OZG identity.

\subsubsection{Overview}

\begin{center}
    \includegraphics[width=8cm]{Diagrams/Integration 1 Overview.png}
\end{center}

\subsubsection{Functionalities}

The IMP client should be able to:
\begin{itemize}
    \item manage personal information stored in the user profile
    \item receive and send messages through the inbox of the user profile
    \item upload and download documents through the data wallet of the user profile
    \item manage active applications
\end{itemize}

The IMP client should however not be used to search for administrative services, as this is a service of the portal which is not related to the management of an identity.

\subsubsection{Integration}

\paragraph{Association IMP ID and OZG ID}

Before the IMP client can access services of the administration portal, it has to be possible to connect the IMP identity with a user profile. The user should be able to connect and disconnect the identity with an existing user profile. As in this scenario the IMP systems only integrate with the administration portal, the user profile should not be modified to include information about an IMP identity.

\begin{center}
    \includegraphics[width=8cm]{Diagrams/Integration 1 Connection Overview.png}
\end{center}

The administration portal can provide an additional web page where a logged in user can connect an IMP identity with his user profile. In order for the web page to initiate a connection process, administration portal and IMP identity require some way to identify each other. Either the IMP identity identifies itself to the administration portal or the administration portal identifies itself to the IMP identity.

The IMP identity could identify itself to the administration portal through manual entering of an IMP ID on the web page. This could enable the administration portal to interact with the identity through a connector. Another option is for the administration portal to identify itself to the IMP identity. As the IMP system provides a functionality for this, it is the better option. Through the connector, the administration portal can create a relationship template. The template is stored on the IMP server but can be accessed by any client which has the correlating template ID. The template contains information for identification of the connector, a encrypted session ID, a reason why the relationship is requested and a list of attributes the IMP client is required to share.

Based on the resulting template ID, the connector creates a QR code which the administration portal includes in web page before sending it to the user. The user can now scan the QR code with the IMP client which retrieves the template corresponding to the template ID from the IMP server. The IMP client displays the request and if the user accepts, the connector is notified of an incoming relationship request. The request contains the template ID, information about the IMP identity of the user, the shared attributes and the encrypted session ID.

The connector transfers the relationship request to the administration portal which based on the decrypted session ID sends a confirmation request to the web page. The confirmation request contains information about the IMP identity which requested to connect to the user profile. If the user accepts the confirmation, the association of the IMP relation and the user ID is stored in a database.

The connection of the user profile and the IMP identity would therefore be an IMP relationship.

\paragraph{Authorisation}

If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token, which enables it to start actions in the name of the user. The user might want to manage which actions an IMP client is authorised for.

On the web page where the user can connect user profile and IMP identity, authorisation of a connection can be managed too. After a success full connection, the web page presents a UI where the user can determine which actions the IMP client should be able to perform. If the user finishes, the administration portal can request the authorisation from the user profile which requests authentication from a user. The resulting JSON Web Token is then transmitted to the administration portal.

The JSON Web Token contains information to identify the user profile and the authorisations for the entity which possesses this token. It also includes a signature with a private key of the user profile component. This allows the component to check if the token is valid.

This token can be stored in the database where IMP relations are mapped to profile IDs.

\paragraph{Improved Association of IMP ID and OZG ID}

JSON Web Tokens can also function as a connection between user profile and IMP identity because they includes the ID of a user profile. If the IMP client is in possession of this token and requests the administration portal to perform an action, the administration portal can read the profile ID stored inside the token along with the authorisation information. The portal can then verify the validity of the token through the user profile component. If the validation was successful, the portal knows, that whoever sent the request has the authorisation stored in the token for the user profile ID stored in the token.

The JSON Web Token can be saved as attribute of the IMP identity which the administration portal was granted access to. Whenever the portal receives a request from a relation to for example modify an attribute in the user profile, the portal can read the JSON Web Token of the corresponding IMP identity determine the connected user profile ID and verify the authorisation.

\paragraph{Personal Information}

One of the goals of an IMP system is to enable the user to only manage his identity in one place while all other service providers rely on the attributes of the identity. As in this scenario however, the OZG system does not rely on attributes of the IMP system but enables it to manage personal information stored in the user profile. Some synchronisation mechanism can therefore operate.

When the user profile is connected with the IMP identity, an attribute request is issued at least for the JWT issued by the user profile component. In case the JWT authorizes the IMP client to manage personal information of user profile, the administration portal can request access to attributes of the IMP identity which are also stored in the user profile.

As the attributes stored in the user profile might be named differently than the attributes stored in the user profile, some mapping has to take place.

The access of the administration portal to attributes of the IMP identity is stored as part of the relationship.

There are multiple ways to synchronize the attributes. One way would require the administration portal to compare the attributes of the IMP identity with those of the user profile. Another option would be for the IMP client to notify the administration portal of a change in the shared attributes. The second option would be beneficial, as iterative requests to the IMP Client and user profile are resource intensive, especially for a large number of users.

\paragraph{Attribute Mapping}

\paragraph{Inbox}

Both IMP Client and the administration portal provide an inbox functionality. If an IMP identity is connected with a user profile, it can send and receive messages as part of the relation it has with the administration portal. As the administration portal does not store any information on which user profile is connected with which IMP identity, it cannot forward messages of the inbox to the IMP identity of a relation. The IMP client will have to request for new messages from time to time or the previously removed database which maps IMP relations to user profiles is added again.

\section{Extension: Inbox}

\section{Extension: Collaboration}

>>>>

\paragraph{1. Create User Profile}
The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.

@@

\paragraph{3. Selection of Administrative Service}
The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

\paragraph{4. Filling in Application}
Personal information from the user profile is used by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

@@

\paragraph{8. Management of Applications}
The administration portal stores active applications and enables the user to manage them.

\paragraph{9. Communication}
As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.  Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.

@@

\begin{figure}[h]
\caption{Overview IMP System}
    \centering
    \includegraphics[scale=0.25]{Diagrams/OZG System Overview.png}
\end{figure}

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components. The most important components, the service facade provides an interface for are:

\begin{itemize}
    \item \textbf{Responsibility Finder}

    This service component is used to find administrative institutions which are responsible for an application. Depending on the type of application and on the home address of the user, different institutions might be responsible.

    \item \textbf{Process Management}

    This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.

    \item \textbf{Search}

    This service component creates a list of URLs of administrative services relevant for a specified search term. This enables the portal to provide a search functionality of administrative services for the user.

    \item \textbf{User Profile Management}

    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and sent messages to an institution.

    \item \textbf{Application Management}

    This service component manages applications issued through the administration portal through communication with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track about the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

@@

@@

\section{IMP System Proposal}
There exist many ways to realize an IMP system. Based on the previously analyzed requirements of users and OZG systems, a possible solution for an IMP system is presented.

\subsection{Components}
The IMP system operates on three domains and consists 3 system components. The user domain contains systems, a user directly interacts with. As for the system architecture of the OZG, can be a web browser. The solution for the IMP system provides an IMP client as an app for smartphones. The IMP domain contains systems hosted by the IMP provider. The IMP server is part of this domain. The Service Provider domain contains the system architecture of the service provider and integration components of the IMP solution.
In the following sections, IMP client and IMP server are explained in more detail, the integration system will be the focus of the next chapter.

\begin{figure}[h]
\caption{Overview IMP System}
    \centering
    \includegraphics[scale=0.25]{Diagrams/IMP System Overview.png}
\end{figure}

@@

The IMP client is a smartphone application which enables the user to manage his IMP identity. It enables the user to:

\paragraph{Create an IMP identity}

After the user installs the application on his smartphone, he is able to create an IMP identity. The identity consists of a public and private key-pair. The private key will never leave the smartphone. The public key is shared with the IMP server along with information on how to communicate with the client.

\paragraph{Manage Attributes}

The user is able to add, remove, update and read any key-value pair as an attribute of his identity. Attributes are encrypted with the

\paragraph{Documents}

The user is able to add, remove, update and read any document as an attribute of his identity. All documents are stored on the smartphone.

\paragraph{Send and Receive Messages}
\paragraph{Send and Receive Relationship Requests}
\paragraph{Send and Receive Share Requests}
\paragraph{Display Forms}

\subsubsection{IMP Server}
The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
\begin{itemize}
    \item Store identities
    \item Create and store relationship template
    \item Create and store request template
    \item Deliver relationship requests
    \item Deliver requests
    \item Deliver messages
\end{itemize}

\subsection{Functionalities}
As already introduced, the IMP solution provides the user with multiple functionalities. In this section, important features are described in more detail.

\subsubsection{Relationship}

IMP identities can establish an IMP relationship. Through this relationship, both identities can securely share attributes and communicate.

To establish a relationship, a relationship template is required. The template is created by an identity which wants to receive relationship requests and is shared with the identity which wants to request a relationship. The relationship template is stored on the IMP server and can be retrieved trough template ID. Besides technical information, the template usually contains:
\begin{enumerate}
    \item Information which the templator would like to share about itself 
    \item Information which the templator would like the requestor to share
    \item Requested additional information about the requestor 
    \item Meta information 
\end{enumerate}

\subsubsection{Share Attribute}

\subsubsection{Change Attribute}

@@

The goal of the integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. The main OZG functionalities are:
\begin{enumerate}
    \item{Create User Profile}
    \item{Login to User Profile}
    \item{Selection of Administrative Service}
    \item{Filling in Application}
    \item{Submission of Application}
    \item{Reception of Application by Administration Portal}
    \item{Submission of Application to Data-Exchange Platform}
    \item{Management of Applications}
    \item{Communication}
\end{enumerate}

@@

\section{Integration Architecture 1}

Integrating an IMP solution for management of customer identities is no simple task. To make the introduction of IMP systems easier for service providers, this first integration architecture describes a non invasive integration. After applying this integration, all OZG services are still usable as before but can be enhanced by IMP solutions. For this integration not to be invasive, only one connector exists and integrates only with the administration portal. No other OZG system component is modified or directly accessed.

The goal of the integration is to enhance each step of the basic OZG use case through integration with IMP solutions. Therefore in the overview section, for each step, possible integration's of OZG systems are evaluated. The following sections contain more detailed descriptions of the selected integration strategies.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
\end{figure}

\subsection{Overview}

This section gives an overview of integration possibilities for each step of the basic OZG use case. For each step, multiple integration strategies are evaluated and one strategy is selected for more detailed description in following sections.

\paragraph{Create User Profile}

The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.

Creation and management of multiple user profiles quickly becomes a burden for users. If all service providers would switch to using only identities provided by an IMP solution, users would only have to manage one digital identity. However performing this change is no simple task for a service provider. An abrupt change of the system architecture can lead to many problems like extended periods of down times. This integration architecture therefore focuses on a simplified initial integration of IMP identities where OZG user profiles can still be used to access OZG services.

It would be possible to integrate the IMP identity as an alternative to the user profile. The user could then use OZG services either by creating a user profile or by providing an IMP identity. Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile. The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management. The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution. OZG systems would have to request personal information from the IMP identity while providing a reason for doing so. After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity. However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile. As the focus of this integration architecture is simplicity and non incisiveness, the connection of IMP identity and user profile is preferred.

The IMP solution provides a service for establishing a connection between entities. It is called an IMP relationship. Through a relationship, two entities can identify each other, assume authentication of the other party and can securely communicate and share attributes of their IMP identities. To utilize an IMP relationship between the administration portal and the IMP identity as connection between user profile and IMP identity, the relationship has to contain identification of the user profile in form of for example a user ID. The administration portal would then be able to map relationships along with the IMP identity ID to user profiles.

In order for an IMP identity to request a relationship with the administration portal, the portal has to provide a relationship template to the IMP client of the user. The template can be made accessible to the IMP client trough a new web page which displays the template ID as QR code if the user is logged in. Each time a logged in user requests the web page, the web server requests the IMP connector to create a relationship template.

The IMP connector provides an API for creation of relationship templates as part of its REST interface. Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response. The web page can then render the template as a QR code on the web page.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template REST.png}
\end{figure}

This is one example, where the OZG system could use the REST interface for integration with the IMP system. However, messaging can improve the integration solution to be more maintainable, stable and scalable and will be the preferred option in following scenarios. Using messaging, the web server can publish a message containing the request for a new relationship template on a "Relationship Template Request" channel, where the connector receives it, creates the template and publishes a reply message containing the template ID on the "Relationship Template Reply" channel.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging.png}
\end{figure}

It could happen, that in future, the API of the connector changes. If the web server integrated the connector through its REST interface, this would require the request code of the web server to be changed. If messaging is used, messages leaving the "Relationship Template Request" channel could be mapped to the new API signature through an additional messaging component called message translator. This is an example for how a messaging can improve maintainability of an integration architecture.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging Improved.png}
\end{figure}

When the user is presented with the web page containing the QR code, the user can scan it with its IMP client. Based on the template ID, the client retrieves the template from the IMP server and displays it for the user. If the user accepts the template, the client sends a relationship request to the IMP server, who forwards it to the corresponding connector.

Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request. If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request. The server would have to regularly request a status update which is not efficient. Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified. The administration portal can process the relationship request and publish a message containing a response on the "Relationship Request Response" channel, where the connector will be notified. Through the IMP server, the connector sends the response to the IMP client and the relationship is established.
In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Request.png}
\end{figure}

Neues Kapitel/Überschrift: Attribute Synchronization

The goal of the connection of IMP identity and OZG user profile is to enable management of personal information through the IMP client. Attributes stored as part of the IMP identity and attributes stored as part of the user profile have to be manageable through the IMP client.

One option would be for the IMP client to overwrite all attributes of the OZG user profile with those stored in the IMP identity and update values in the user profile as soon as an attribute of the IMP identity changes. This would require the user profile management web page of the administration portal to be locked for profiles with a connected IMP identity. Another option would be to enable the user to manage attributes of IMP identity and user profile separately through the IMP client.

The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically. However, this would require the user to always share the most current personal information with the OZG systems. Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider. If the user for example changes the home address of its IMP identity, the OZG system might not want to approve this change immediately. If the user manages IMP identity and user profile separately, changes of the OZG user profile can happen on a request reply basis. The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there. The disadvantage of this option is, that the management of personal information is more complicated than the first option. Through attribute management tools on the IMP client, the experience can be improved.

As the second option provides necessary features, which the first option does not have, it is preferred.

The management of both IMP identity attributes and attributes of the OZG user profile can be done as part of the relationship established for their connection. As part of the connection, IMP identity and administration portal share attributes. The user profile can be determined to store the exact same values as shared by the IMP identity as part of this relationship. Therefore, in order to change attributes of the user profile, the value of the shared attributes has to change. This can be done through a request-reply process. One party requests the change of a shared attribute, which will only be done if the other party accepts. This enables the user to manage the OZG user profile through the IMP client by requesting a change for attributes shared as part of a relationship. The user could also manage his user profile through the web page of the administration portal, resulting in a request form the administration portal to change shared attributes of the relationship.

As administration portal and IMP identity established a relationship, the connector can be excluded from the diagram for better visualisation. Behind the scenes, all interactions between administration portal and IMP client still go through connector and IMP server.

If the user requests the change of a shared attribute through the IMP client, it sends an attribute change request to the administration portal by publishing a message on the "Inbound Attribute Change Request" channel. After the administration portal decides to accept the request, it can publish a message to the "Outbound Attribute Change Response" channel. This message will on one hand be received by the IMP client and on the other hand result in an update of the user profile.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change IMP Client.png}
\end{figure}

If the user requests the change of a shared attribute through the web page of the administration portal, the web server sends an attribute change request to the "Outbound Attribute Change Request" channel which is received by the IMP client. If the user accepts the request, the client publishes a message on the "Inbound Attribute Change Response" channel where it results in an update of the user profile.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change Web Page.png}
\end{figure}

\paragraph{Login to a User Profile}

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal. As the integration solution for connection of user profile and IMP identity was chosen, the user is still able to login to his user profile on the administration portal and take advantage of all OZG services. The IMP system can however provide an additional way to access OZG services through the IMP client. One possibility was already introduced: the management of personal information.

In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid. Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session. When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components. This process is necessary because any person can send requests to the web server and possibly pretend to be a different user. In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user. Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity. As the IMP client is an app installed on the smartphone of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Login.png}
\end{figure}

\paragraph{Application for Administrative Service}
The third step is selection of an administrative service through the web page of the administration portal. This service is not directly related to identity management and will therefore not be provided by the IMP client.
The steps four to eight are not integrated by the IMP solution as this would require invasive interaction with components other than the administration portal.

As a result of that, most of the steps necessary for applying for an administrative service remain to be done through the web page of the administration portal with a logged in user profile. The next integration architecture will present a solution where most of the steps will be done through the IMP systems.

\paragraph{Communication}

The ninth step of the basic OZG use case is to communicate with responsible institutions. As both the user profile and the IMP identity provide an inbox, the IMP client can be used to send and receive messages through the inbox of the OZG user profile.

The messages related to a OZG user profile can be exchanged as part of the relationship between the administration portal and the IMP identity. Messages received by the user profile can be forwarded by the administration portal to the inbox of the IMP identity. Sending messages from the IMP client to institutions however is not possible, as the IMP client does not know the address of the institution responsible for an application. However, if the IMP client already received a message from an institution, it can enable the user to respond.

\subsection{Connection}

\subsection{Personal Information}

\subsection{Authentication}

\subsection{Communication}

\section{Integration Architecture 2}

The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 2/Overview.png}
\end{figure}

\subsection{Overview}

The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal. This is not necessary any more, as user profiles are replaced by IMP identities. The user will only have to create an IMP identity.

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal. As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services. The IMP client does not require authentication, as it is installed on the smart phone of the user. The user can secure his smartphone through for example biometric authentication.

The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.

The fourth step of the basic OZG use case is to fill in the application. The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.

The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more. Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.

For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template. The connector responds to the institution with the template IDs.

In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address. After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.

If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it. The relationship template contains a description of the selected administrative service as reason for the relationship. The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application. This replaces the functionalities of the form server.

The fifth step of the basic OZG use case is to submit the application. After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes. The institution can accept the request and start processing the application. The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.

The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.

The eighth step of the basic OZG use case is the management of active applications. As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution. Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.

The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications. As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.
